### 2016-05-25 paper/icfp16-cameraready/evaluation.tex
fix formatting of plots

\paragraph{Benchmarks}
We answer these questions on two sets of ill-typed programs, \ie
programs that were rejected by the \ocaml\ compiler because of a
type error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at our institution.
%
We recorded each interaction with the \ocaml\ top-level system over the
course of the first three assignments (IRB  
\# hidden for blind review), 
% \#140608),
from which we extracted \ucsdsize\ distinct, ill-typed \ocaml programs.
%
The second dataset --- widely used in the literature --- comes from a
graduate-level course at the University of Washington~\cite{Lerner2006-pj},
from which we extracted 284 ill-typed programs.
%
Both datasets include programs that demonstrate a variety of functional
programming idioms, including (tail) recursive functions, higher-order
functions, polymorphic data types, and expression evaluators.

>>>>

\paragraph{Benchmarks}
We answer these questions on two sets of ill-typed programs, \ie
programs that were rejected by the \ocaml\ compiler because of a
type error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at UC San Diego.
%
We recorded each interaction with the \ocaml\ top-level system over the
course of the first three assignments (IRB  
% \# hidden for blind review),
\#140608),
from which we extracted \ucsdsize\ distinct, ill-typed \ocaml programs.
%
The second dataset --- widely used in the literature --- comes from a
graduate-level course at the University of Washington~\cite{Lerner2006-pj},
from which we extracted 284 ill-typed programs.
%
Both datasets include programs that demonstrate a variety of functional
programming idioms, including (tail) recursive functions, higher-order
functions, polymorphic data types, and expression evaluators.
